\noindent\textbf{RESEARCH PROPOSAL:}

\bigskip

\noindent\begin{tabularx}{\textwidth}{|>{\columncolor{tcc}}X|}
\hline
In this section, you must incorporate the following aspects:
\begin{enumerate}[label={\alph*)},nosep]
\item Theoretical-conceptual and state-of-the-art developments that underpin the proposal
\item Objectives and hypotheses or research questions
\item Methodology
\item Work Plan, schedule and Gantt chart
\item Background information to assess the capacity of the team to implement the proposal
\item Scientific or technological novelty of your proposal
\end{enumerate}

\medskip

Remember that:
\begin{itemize}[label={-},nosep]
\item All text, paragraphs or textual phrases from a bibliographic reference, whether by other authors or their own, must be duly identified in the text and in the list of references.
\item You must strictly comply with what is established in the Guidelines of the 2022 Regular National Competition.
\end{itemize}

\medskip

This file must contain a maximum of \textbf{10 pages} (use letter size format, Verdana font size 10 or similar).\\
\hline
\end{tabularx}

\section{Theoretical concepts and state of the art}

Blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah.

Some math: $\frac{x}{\sqrt{1-x^2}}$.

\begin{equation}\label{Euler}
\exp(\imath\theta) = \cos(\theta) + \imath \sin(\theta).
\end{equation}

We can refer to equations like this: \eqref{Euler}.
We can do refer to bibliography entries like this \cite{AF:2003} or this \cite{CEL:arXiv, MS}.

\subsection{A subsection}

Blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah.

Blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah.

\subsection{Another subsection}

Blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah.

Blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah.

\section{Objectives and Hypotheses}

\subsection{Hypotheses}
\begin{enumerate}
\item An hypothesis.
\item Another hypothesis.
\end{enumerate}

\subsection{Objectives}
\begin{enumerate}
\item First objective.
\item Second objective.
\item Third objective.
\end{enumerate}

\section{Methodology}

Blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah.

\section{Work Plan, schedule and Gantt chart}

\subsection{Work Plan}

Blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah.

\subsection{Schedule}

\begin{itemize}
\item Apr 1st, 2022: Start work on objective 1.
\item May 23rd, 2023: Start work on objective 2.
\item Dec 18th, 2023: Finish work on objective 1.
\item Jul 14th, 2024: Start work on objective 3.
\item Feb 8th, 2025: Finish work on objective 2
\item March 31st, 2026: Finish work on objective 3.
\end{itemize}

\subsection{Gantt chart}

\begin{ganttchart}[
expand chart=\textwidth,
time slot format=isodate,
title label font=\scriptsize
]{2022-04-01}{2026-03-31}
\gantttitlecalendar{year,month}\\
\ganttbar{Objective 1}{2022-04-01}{2023-12-18}\\
\ganttbar{Objective 2}{2023-05-23}{2025-02-08}\\
\ganttbar{Objective 3}{2024-07-14}{2026-03-31}
\end{ganttchart}

\section{Background information to assess the capacity of the team to implement the proposal}

Blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah.

\section{Scientific or technological novelty of the proposal}

Blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah.
